Project Light

### 2015-09-09 paper/paper.tex
add bibtex sources and use them in some notes

\keywords{awesome, keywords, go, here}

@@

\section{Related Work}
\label{sec:related_work}

@@

Project Light consists of an Android app that creates and sends the keying material and a Contiki process that runs on the TelosB sky mote and receives and validates it.
Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.

>>>>

\keywords{Internet of things, security, key transmission, light}

@@

\section{Background and Related Work}
\label{sec:related_work}

- first background of our work, than alternative solutions

\subsection{Background}

- background:
	- "Standardized Protocol Stack..."\cite{palattella2013standardized} describes network stack for iot, maybe implemented in contiki
	- akes\cite{krentz15akes}
- related work:
	- webseite mit flickerer\cite{electricimp}
	- LiDSN\cite{doan2012lidsn}
	- message in a bottle\cite{kuo2007message}: init keys within Faraday cage, jam radio with outside device
	- Blink ’Em All\cite{saxena2009blink}: communication via light, but other way round: motes blink and camera parses it.
	- "Over the Air Provisioning..."\cite{chen2011over} uses eliptic curve crytpography, which needs a lot of space on the mote
	- smart sys tech 2015\cite{krentz20156doku}:
		- 6Doku protocol --> successor of sudoku protocol (diffie hellman, etc.)
		- touch-device with 6lowpan transmitter as (mother duck)
		- press butttons on motes and touchscreen on mother duck --> pair them
		-

@@

Project Light consists of an Android app that creates and sends the keying material and a Contiki\cite{dunkels04contiki} process that runs on the TelosB sky mote and receives and validates it.
Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.
